Data Migration under a Changing Schema in Ampersand

### 2023-10-30 2022Migration/articleMigrationFACS.tex
minor

\section{Generating a Migration Script}
\label{sct:Generating}
   The complexity of migrating data to date yields expensive and error-prone migration projects.
   For that reason, we want to generate this code.
   To ensure the correctness of the generator is even more challenging.
   That is why we have proven the correctness of the generator in Isabelle/HOL.

@@

\subsection{Algorithm for generating a migration script}
   (\@Bas, I have added the relevant portions of {\tt Kurk.adl} as \LaTeX\ comments near every equation in the \LaTeX\ source,
   so we can guard their correspondence.)

>>>>

\section{Generating a Migration Script}
\label{sct:Generating}
   The complexity of migrating data to date yields expensive and error-prone migration projects.
   By generating this code we can eliminate human induced errors.
   We enhance the quality of the generator further by proving its correctness in Isabelle/HOL.

@@

\subsection{Algorithm for generating a migration script}
   (\@Bas, ik heb de relevante delen van {\tt Kurk.adl} als \LaTeX\ commentaar bij elke equation in de \LaTeX\ broncode toegevoegd,
   zodat we in de gaten kunnen houden dat ze met elkaar overeenkomen.)
